Econ Analysis

### 2020-03-04 Ecology/Manuscript_Draft.Rmd
Re-organized repository

---
title: "Challenges to transboundary fisheries management in North America under climate change"
author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
subtitle: "[Response to Reviewers]"
date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
output:
  word_document: default
  pdf_document: default
bibliography: References/Oceans_Canada_Bibliob.bib
editor_options: 
  chunk_output_type: console
csl: References/harvard.csl
---

>>>>

---
title: "Challenges to transboundary fisheries management in North America under climate change"
author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
subtitle: "[Response to Reviewers]"
date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
output:
  word_document: default
  pdf_document: default
bibliography: References/Oceans_Canada_Biblio.bib
editor_options: 
  chunk_output_type: console
csl: References/harvard.csl
---

### 2020-03-04 Econ/Econ_Analysis.Rmd
Re-organized repository

EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")

EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

@@

# From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
Raw_DBEM_Results <- data.table::fread("~/Documents/UBC/Oceans_Project/Manuscript/Data/Raw_Data.csv") %>% 
  filter(Species != "Anoplopoma fimbria") #Remove

@@

####_____ IPHC Data ####
# Data from IPHC https://iphc.int/data/commercialresearch-landing-weights-datasets
# Data in metric tonne
IPHC_Landings <- read_excel("~/Documents/UBC/Oceans_Project/Econ/Data/IPHC/iphc-19912017-commres.xlsx", 
                                    col_types = c("numeric", "text", "text", 
                                                  "numeric", "numeric", "numeric", 
                                                  "text"), skip = 2)
# Clean  landings

@@

# 
GoM_Landings <- read.csv("~/Documents/UBC/Oceans_Project/Econ/Data/SAU_Landings/GoM/SAU MEOW 55 v47-1.csv")

@@

Fishing_Cost <- read_excel("~/Documents/UBC/Oceans_Project/Econ/Data/Economic/FishingCost_USA_Canada_20Feb2017.xlsx", 
                           col_types = c("text", "text", "text", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric"), 
                           skip = 1)

@@

Ex_Vessel <- read.delim("~/Documents/UBC/Oceans_Project/Econ/Data/Economic/Price_US_Canada_5spp.csv")

@@

Profit_Data_Paper <- Profit_Data_Weight %>% 
  mutate_at(vars(Cost_perTon_2010,Price_perTon,Profit_perTon),
            funs(round((.*Avrg_Landings)/1000000,2)) # million USD
            ) %>% 
  group_by(EEZ,Species) %>% 
  summarise_if(is.numeric,sum,na.rm=T)

@@

@@

@@

# Save plot 
ggsave("Econ_Plot.tiff",
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = "./Results")
```

>>>>

EEZIDs_List <- read_excel("./Econ/Data/Spatial/Updated_EEZList_17June2016.xlsx")
EEZ_CellID <- read_excel("./Econ/Data/Spatial/EEZ_CellID.xlsx")
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread("./Econ/Data/Spatial/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

@@

# From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
Raw_DBEM_Results <- data.table::fread("./Ecol/Data/Distribution/Raw_Data.csv") %>% 
  filter(Species != "Anoplopoma fimbria") #Remove

@@

####_____ IPHC Data ####
# Data from IPHC https://iphc.int/data/commercialresearch-landing-weights-datasets
# Data in metric tonne
IPHC_Landings <- read_excel("./Econ/Data/IPHC/iphc-19912017-commres.xlsx", 
                                    col_types = c("numeric", "text", "text", 
                                                  "numeric", "numeric", "numeric", 
                                                  "text"), skip = 2)
# Clean  landings

@@

# 
GoM_Landings <- read.csv("./Econ/Data/SAU_Landings/GoM/SAU MEOW 55 v47-1.csv")

@@

Fishing_Cost <- read_excel("./Econ/Data/Economic/FishingCost_USA_Canada_20Feb2017.xlsx", 
                           col_types = c("text", "text", "text", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric", "numeric", 
                                         "numeric", "numeric"), 
                           skip = 1)

@@

Ex_Vessel <- read.delim("./Econ/Data/Economic/Price_US_Canada_5spp.csv")

@@

Profit_Data_Paper <- Profit_Data_Weight %>% 
  mutate_at(vars(Cost_perTon_2010,Price_perTon,Profit_perTon), # note these are totals and not per tone
            funs(round((.*Avrg_Landings)/1000000,2)) # million USD
            ) %>% 
  group_by(EEZ,Species) %>% 
  summarise_if(is.numeric,sum,na.rm=T)

@@

### Alternative landed values

# Canada Flounder 134 tonnes for $81,093 = $/t 605

# Canada Cod 5,982 tonnes for $7,007,566	= $/t 1171.442

@@

# Figure 1

@@

# Save plot 
ggsave("Econ_Plot.tiff",
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = "./Results")

# Figure 2 / Table 2

ggplot() +
  geom_line(data = Average_Prop_Plot,
            aes(
              x=Time_Sector,
              y=Discounted_Profits_mean, # Percentage
              colour=EEZ
            )
  ) +
  geom_errorbar(data = Average_Prop_Plot,
                aes(
                  x=Time_Sector,
                  ymin=(Discounted_Profits_mean-Discounted_Profits_sd), # mean +- 2*sd
                  ymax=(Discounted_Profits_mean+Discounted_Profits_sd),
                  colour=EEZ
                ),
                # alpha=0.5,
                width=.1,
                # position=position_dodge(0.05),
                size = 0.6
  ) +
  geom_line(data = Average_Prop_Plot,
            aes(
              x=Time_Sector,
              y=Non_Discounted_Profits_mean, # Percentage
              colour=EEZ
            ),
            alpha = 0.5,
            linetype = "dashed"
  ) +
  geom_errorbar(data = Average_Prop_Plot,
                aes(
                  x=Time_Sector,
                  ymin=(Non_Discounted_Profits_mean-Non_Discounted_Profits_sd), # mean +- 2*sd
                  ymax=(Non_Discounted_Profits_mean+Non_Discounted_Profits_sd),
                  colour=EEZ
                ),
                alpha=0.5,
                width=.1,
                # position=position_dodge(0.05),
                size = 0.6,
                linetype = "dashed"
  ) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_colour_manual(values = wes_palette("IsleofDogs1")) +
  scale_x_continuous(breaks=c(1, 2, 3),
                     labels=c("Present-day", "Mid-century", "End-century")) +
  # ylim(0,100)+
  facet_grid(Species ~ RCP,
             labeller = labeller(Species = Common_Names),
             scales = "free"
  ) +
  labs(
    x = "",
    y = "Profits"
  ) +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 18),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 12),
    strip.text = element_text(size = 16),
    panel.spacing.x = unit(3.5, "lines")
  )

# Save plot 
ggsave("Econ_Plot_2.tiff",
       plot = last_plot(),
       width = 10,
       height = 8,
       units = "in",
       path = "./Econ/Results")
